---
title: "Assignment2"
author: "Yineng Chen"
date: "7/6/2020"
output: ioslides_presentation
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(plotly)
library(tidyverse)
```

## Description

I'm going to focus on the Airbnb data in Manhattan for this Assignment.These data were accessed from [Inside Airbnb](http://insideairbnb.com/get-the-data.html) on July 5th, 2020. The version of the data that we will use in this class can be found [here](http://data.insideairbnb.com/united-states/ny/new-york-city/2020-06-08/visualisations/listings.csv).

The data set contains NYC airbnb data including type of room, price, location, avaiability etc.

## Data discription

 After loading the data, the resulting R data file `airbnb` contains a single dataframe with 21,963 rows of data on 16 variables:

- id: listing id
- name: listing name
- host_id: host id
- host_name: host name
- neighbourhood_group: NYC borough
- neighbourhood: NYC neighborhood
- latitude: listing latitude

***

- longitude: listing longitude
- room_type: type of listing (Entire home/apt, Private room, Shared room)
- price: listing price
- minimum_nights: required minimum nights stay
- number_of_reviews: total number of reviews
- last_review: date of last review
- reviews per month: average number of reviews per month
- calculated_host_listings_count: total number of listings for this host
- availability_365: number of days listing is available out of 365

## Plotly

This plot shows the price of different room type.

```{r}
manh_airbnb = read_csv("./listings.csv", col_types = c("ccccccddfdddDddd")) %>% filter(neighbourhood_group == "Manhattan")


plot_ly(manh_airbnb, y = ~price, color = ~room_type, type = "box")
```


