---
title: "Assignment1"
author: "Yineng Chen"
date: "7/5/2020"
output: 
  html_document:
    keep_md: true
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(leaflet)
library(tidyverse)
```

## Description

I'm going to focus on the Airbnb data in Manhattan for this Assignment.These data were accessed from [Inside Airbnb](http://insideairbnb.com/get-the-data.html) on July 5th, 2020. The version of the data that we will use in this class can be found [here](http://data.insideairbnb.com/united-states/ny/new-york-city/2020-06-08/visualisations/listings.csv).

## Data discription

The data set contains NYC airbnb data including type of room, price, location, avaiability etc. 

After loading the data, the resulting R data file `airbnb` contains a single dataframe with 21,963 rows of data on 16 variables:

```{r, include=FALSE}
manh_airbnb = read_csv("./listings.csv", col_types = c("ccccccddfdddDddd")) %>% filter(neighbourhood_group == "Manhattan")
```

- id: listing id
- name: listing name
- host_id: host id
- host_name: host name
- neighbourhood_group: NYC borough
- neighbourhood: NYC neighborhood
- latitude: listing latitude
- longitude: listing longitude
- room_type: type of listing (Entire home/apt, Private room, Shared room)
- price: listing price
- minimum_nights: required minimum nights stay
- number_of_reviews: total number of reviews
- last_review: date of last review
- reviews per month: average number of reviews per month
- calculated_host_listings_count: total number of listings for this host
- availability_365: number of days listing is available out of 365


## Map

The map shows the name, location, Price and room type of Airbnb houses in Manhattan.

```{r}
popupmessage = paste("Name:", as.character(manh_airbnb$name), "<br>",
                     "Room Type:", as.character(manh_airbnb$room_type), "<br>",
                     "Price:", as.character(manh_airbnb$price), "<br>")


manh_airbnb = manh_airbnb %>% mutate(color = "pink")


getColor <- function(manh_airbnb) {
  sapply(manh_airbnb$room_type, function(room_type) {
  if(room_type  == "Private room") {
    "red"
  } else if(room_type  == "Entire home/apt") {
    "lightgreen"
  } else if(room_type  == "Shared room") {
    "lightblue"
  }else {
    "pink"
  } })
}

icons <- awesomeIcons(
  icon = 'ios-close',
  iconColor = 'white',
  library = 'ion',
  markerColor = getColor(manh_airbnb)
)



manh_airbnb %>% 
  leaflet() %>%
  setView(lng = -73.9712, lat = 40.7831, zoom = 12) %>% 
  addTiles() %>%
  addAwesomeMarkers(clusterOptions = markerClusterOptions(),
             popup = popupmessage,icon=icons) %>% 
  addLegend(labels = c("Private room","Entire home/apt","Shared room","Hotel room"), colors = c("red", "lightgreen", "lightblue","pink"))
  
```



