---
title: "Yineng's Presentation"
author: "Yineng Chen"
date: "7/4/2020"
output: ioslides_presentation
---

```{r setup, include=FALSE}
# knitr::opts_chunk$set(echo = FALSE)
```

## Introduction

### Myself

- Name: Yineng Chen

- Age: 24

#### My hobbies

1. Movies
2. Food

### My School

- columbia

***
A Slide without title

### **Format**

*qwer*

**Bound**

`summary(cars)`

summary(cars)

## Options for R code 

### Run the code but does not show it : echo = FALSE

The default is echo = FALSE. Delet it to show codes without run the codes.

```{r, eval=FALSE}
summary(cars$speed)
```


### Show the code and run it: echo=TRUE

```{r, echo=TRUE}
summary(cars$speed)
```

## Options for R code 

### Get rid of #s in the output:  comment=""

```{r, echo=TRUE, comment=""}
summary(cars$speed)
```


### Show the code but do not run it:eval= FALSE

```{r, eval= FALSE}
head(airquality)
```





## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```

## Slide with Plot

```{r pressure}
plot(pressure)
```

